\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            pdftitle={Lab 03},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=Blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}


  \title{Lab 03}
    \author{}
    \date{}
  

% change section title styling
\usepackage{sectsty}
\sectionfont{\normalsize\normalfont\itshape}
\subsectionfont{\normalsize\normalfont}

% use fancyhdr style
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead[LO, LE]{Lab 03}
\fancyhead[RO, RE]{GEOG 432/832}
\makeatletter
\renewcommand{\maketitle}{\bgroup\vspace*{-1cm}\setlength{\parindent}{0pt}
\begin{flushleft}
  \@author
  
  \@date
  
\end{flushleft}\egroup
}
\makeatother

\begin{document}
\maketitle

\hypertarget{lab-03-spatial-and-tabular-analysis-in-arcgis-pro}{%
\section{Lab 03: Spatial and tabular analysis in ArcGIS
Pro}\label{lab-03-spatial-and-tabular-analysis-in-arcgis-pro}}

\hypertarget{read-the-instructions-completely-before-starting-the-lab}{%
\subsubsection{Read the instructions COMPLETELY before starting the
lab}\label{read-the-instructions-completely-before-starting-the-lab}}

This lab builds on many of the discussions and exercises from class.
There is no introductory exercises or background information. Complete
the tasks below and answer the questions that follow. As always, there
are multiple ways accomplishing the task(s) at hand.

The following tasks use the feature classes found in the
``lab03data.zip'' file on Canvas. - Census file - DESCRIPTION - NHDPlus
dataset - DESCRIPTION with FIELDS OF INTEREST\ldots{} NEED the file with
urban, forest, and agriculture - Lake Champlain

\hypertarget{task-1-analyze-a-hydrologic-dataset}{%
\subsection{Task 1: Analyze a hydrologic
dataset}\label{task-1-analyze-a-hydrologic-dataset}}

1.1. Write a Python script that finds the NHDPlus segment with the
\emph{second} largest \emph{absolute difference} between phosphorus load
(LOAD OR YIELD)? from agricultural land use and from forested land use.
Your script must use a search cursor.

1.2. Find the top 10 NHDPlus segments by total load (DEFINE HERE).
Export the data to your analysis tool/softwas of choice (e.g., Excel,
R). Create a scatterplot (e.g.,
\url{https://en.wikipedia.org/wiki/Scatter_plot}) with agricultural load
(OR YIELD) on the x-axis and forested land use on the y-axis (OR
YIELD???). You must use a SearchCursor in your script.

1.3. Make another scatterplot. This time, plot the distance from each
NHDPlus segment to Lake Champlain on the x-axis, and plot total load (OR
YIELD??) on the y-axis.

\hypertarget{task-2-nebraska-counties-census-data}{%
\subsection{Task 2: Nebraska counties census
data}\label{task-2-nebraska-counties-census-data}}

2.1 Using an UpdateCursor, delete all counties that do NOT start with
the letter ``L''. Print the names of the remaining counties and their
population of female residents under the age of 5.

2.2 The next tasks is to calculate an index of social vulnerability. For
the sake of this exercise, we will calculate a very simple vulnerability
index with only 2 components \textbf{(note, vulnerability is MUCH, MUCH
more complex)}. We will use the indicators: income (``PerCapInc'') and
the proportion vacant homes (``Vacant'' / ``TotalUnits''). We will
assume vulnerability is \emph{negatively} correlated with income, and
\emph{positively} correlated with vacancy. This means you will need to
account for different directions in the two indicators. Further, we will
assume our initial analysis has shown that income is \emph{twice as
strong of a predictor} of vulnerability as the vacancy rate.
\textbf{Your job:} develop a metric of ``vulnerability'' using these two
indicators. Map the result using a choroplth map. \emph{(Note, I am NOT
concerned that you build the perfect indicator or even understand the
concept of social vulnerability. I want to see that you can think
through indicators of different magnitude, order, and importance.)}

\newpage

\hypertarget{what-to-turn-in}{%
\subsection{What to turn in:}\label{what-to-turn-in}}

\begin{itemize}
\item
  Task 1: your code for 1.1, 1.2, and 1.3, scatterplots form 1.2 and 1.3
\item
  Task 2: your code for 2.1, 2.2, your map from 2.2
\end{itemize}

\hypertarget{answers-to-the-following-question}{%
\subsubsection{Answers to the following
question:}\label{answers-to-the-following-question}}

For task 2.2, describe how you chose to construct your indicator. What
problems did you encounter and how did you solve them? You must address:
1) how you handled the different direction of effects on vulnerability,
2) how you calculated different importance (or ``weights'') of the two
metrics, and 3) how you handled the fact the two metrics are in
different units? Again, there is no right or wrong answer (I know you're
not an expert on vulnerability). Rather, I want you to demostrate
thoughtfulness in your design.


\end{document}